PANCHANGE_data_preprocessing

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
renamed NBR Sample ID
filtered out extra GLAD people from NBR cohort

Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
++MD: 3,410 participants from NBR IBD cohort excluded
```{r COVID exclusion of IBD}
if(NBR == TRUE) {
dim(dat.no.sex.no.gender.no.age)

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age %>%
  filter(Cohort != "IBD")

@@

# Rename NBR Sample ID 
```{r rename NBR sample ID}
if(NBR == TRUE){
dat.coping <- dat.coping %>%
  recode(Sample,
         "SP0068" = "NBR"
         )
}
```

>>>>

Exclusion of inflammatory bowel disease (IBD) and GLAD BioResource (NBR) cohort
++MD: 3,410 participants from NBR IBD cohort excluded
++KT: 3 duplicated GLAD participants are excluded
```{r COVID exclusion of IBD and GLAD from NBR sample}
if(NBR == TRUE) {
dim(dat.no.sex.no.gender.no.age)

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age %>%
  filter(Cohort != "IBD") %>%
  filter(Cohort != "GLAD")

@@

# Rename NBR Sample ID 
```{r rename NBR sample ID}
if(NBR == TRUE){
dat.coping <- dat.coping %>%
  mutate(
    Sample = 
    recode(
      Sample, 
      "SP0068" = "NBR"
    )
  )
}
```
